### 2024-02-12 outputs/paper/paper.qmd
Update Data section

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(palmerpenguins)
```

# Introduction

You can and should cross-reference sections and sub-sections.

The remainder of this paper is structured as follows. @sec-data.... \newpage

# Data {#sec-data}

## Source

The original paper, "The Unequal Distribution of Opportunity: A National Audit Study of Bureaucratic Discrimination in Primary School Access(2020) by Olsen, Kyhse-Anderson, Moynihan", was replicated from American Journal of Social Science.

@fig-decision_rate1 is one of the results in the original study, and it shows the decision type rate based on the different treatments (Muslim/Danish). In addition to the results depicted in @fig-decision_rate1, we proceeded the analysis by incorporating new variables, namely the characteristics of schools.

```{r}
#| echo: false
#| label: fig-decision_rate1
#| message: false
#| fig-cap: Decision type rate based on each treatment
knitr::include_graphics(file.path(here::here(),"outputs/models/replicated_figure.png"))
```

## Overview of Senders and Respondents' traits

In the original experiment, the designed sender attributes consist of two categories: names (Muslim and Danish names) and the Diligence trait. Also, the respondent schools are classified based on six characteristics: whether the school is located in a major city, its geographical region, the average student grades, the number of students, the number of non-Danish students, and the school type. Theses school characteristics were investigated through the Danish Ministry of Education database in the original study. Below is a summary.

[***Senders trait***]{.underline}

-   **Name**:

    -   Danish: Peter Nielsen

    -   Muslim: Mohammad Osman

-   **Diligence trait**:

    Diligence trait was classified based on the content of the emails, according to the experiment setting in the original study.

    -   Hi \[school name\]. I am writing because we would like to move our son to another school.

        [Non-diligent student treatment]{.underline}: He is in 3rd grade and we don't think that it is going very well at this school

        [Diligent student treatment]{.underline}: He is in 3rd grade and the teachers say that he is doing well with his homework. but we still don't think that it is going very well at this school

[***Respondents'(School) trait***]{.underline}

-   **Major(Big) city**: whether the school is located in a big city

-   **Geographical region**: Reion Hovedstade, Region Midtjylland, Region Nordjylland, Region Sjaelland or Region Syddanmark

-   **School type**: Public or Private

-   **Number of Students**

-   **Number of Non-Danish Students**

-   **Average Grade of Students**

## Methodology

As mentioned above, this paper examines how the characteristics of schools, in addition to the original experiment's results for decision type rates, impact Muslim's admission to private schools in Denmark. The following subsection will provide detailed explanations of how and why each piece of data was used or not.

### Decision type

As shown on @fig-decision_rate1, in the original study, the schools' responses were categorized into three decision types: clear rejection, unclear response and clear acceptance. According to the study, two coders categorized each response email into these three decision types, and the responses categorized by two coders were denoted by response1 and response2. As a result, the Cronbach's alpha analysis revealed minimal difference in perception between the two coders regarding the response emails. Therefore, in this paper, only Response type 1 is used, and the they are denoted as reject1, unclear1, accept1 in the data set.

### Using Senders and Respondents' traits

Followed by the Senders and Respondents' trait above, the original study also investigated whether each school is above the median level of trait(Number of Students, Number of Non-Danish Students and Students' grade). Based on this examination, this study examined how schools with above-median and below-median traits influence the decision type rate through proportional contrasts. Additionally, the impact of school location and school type on Muslim's decision type rate will be investigated.

### Not using Diligence trait

Finally, diligence trait is excluded from this study. This decision is based on the original research, which revealed through the full ordinary least square(OLS) results that diligence traits do not have any effect on outcome variables such as response rate or the decision to accept or reject students.

# Results

Our results are summarized in @tbl-modelresults.

# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

# References

### 2024-02-12 inputs/data/ms_tables_figures.R
Save replicated figure3 in model file

@@ -5,7 +5,7 @@
 # Title: The Unequal Distribution of Opportunity: 
 # A National Audit Study of Bureaucratic Discrimination in Primary School Access
 #
-# Authors: Asmus Leth Olsen, Jonas Høgh Kyhse-Andersen and Donald Moynihan                                                                          
+# Authors: Asmus Leth Olsen, Jonas H?gh Kyhse-Andersen and Donald Moynihan                                                                          
 #                                   
 # Summary: Replication code for producing all tables, figures and facts in the main text.    
 #
@@ -23,6 +23,7 @@ library(estimatr)
 library(texreg)
 library(scales)
 library(cowplot)
+library(grid)
 
 ####################
 # Note to the reader
@@ -35,7 +36,7 @@ library(cowplot)
 setwd(dirname(rstudioapi::getSourceEditorContext()$path))
 
 #load data for main analysis
-load("df1.Rda")
+load("inputs/data/df1.rda")
 
 ##########################################################
 # Facts in section 'Abstract' & 'Introduction'
@@ -360,12 +361,11 @@ legend <- get_legend(fig3a)
 fig3a <- fig3a + theme(text = element_text(size=12),legend.position="none",axis.text.x=element_blank()) 
 
 #Saving figure 3 as PNG
-fig3 <- grid.arrange(fig3a, fig3b, fig3c, legend, nrow = 1, widths=c(2, 2, 2, 1))
-ggsave(file = "figure3.png",fig3,width=8,height=4,scale=1)
+fig3 <- grid.arrange(fig3a, fig3b, fig3c, legend, nrow = 1, widths=c(2, 2, 2, 1), top=textGrob("Decision type rate based on each treatment", gp=gpar(fontsize=15,font=8)))
+ggsave(file = "replicated_figure.png",fig3,path = "outputs/models",width=8,height=4,scale=1)
 
 #Saving figure 3 as PDF
 ggsave(file = "figure3.pdf",fig3,width=8,height=4,scale=1)
-
 
 ##########################################################
 # Facts in section 'Decision to Accept or Reject Students'

### 2024-02-12 scripts/replication.R
added two replications

@@ -1,0 +1,142 @@
+# ########################################################################################
+# Purpose: Create 3 replication of table and figures
+# Author: Sachin Chhikara
+# Date: 11 February 2024
+# Replication Package based off the paper: The Unequal Distribution of Opportunity: 
+# A National Audit Study of Bureaucratic Discrimination in Primary School Access
+#
+# Code was inspired by: 
+# Asmus Leth Olsen, Jonas H?gh Kyhse-Andersen and Donald Moynihan replication package                                   
+# Summary: Replication code for producing all tables, figures and facts in the main text.    
+#
+#
+# #########################################################################################
+
+rm(list = ls())
+
+#load packages
+library(tidyverse)
+library(ltm)
+library(gridExtra)
+library(estimatr)
+library(texreg)
+library(scales)
+library(cowplot)
+library(ggplot2)
+
+####################
+# Note to the reader
+####################
+
+# This script is arranged in the order as the figures, tables and facts are presented in the manuscript.
+# A separate codebook provides definition of all variables and their respective values.
+
+##set path for data
+setwd(dirname(rstudioapi::getSourceEditorContext()$path))
+
+#load data for main analysis
+load("df1.Rda")
+
+##########################################################
+# Facts in section 'Abstract' & 'Introduction'
+##########################################################
+
+#N in the main data file
+nrow(df1)
+
+
+##############################################################
+#Table 3: Means for the Dependent Variables across Treatments
+##############################################################
+
+#content of table 3
+#0=Muslim Name, public school
+#1=Muslim Name, private school
+#2=Danish Name, public school
+#3=Danish Name, private school
+
+for (i in 1:length(df1$treatments)) {
+  
+  if (df1$t_mohammad[i] == 1 & df1$school_type[i] == 1){
+    df1$treatments[i] <- 0
+
+  }
+  else if (df1$t_mohammad[i] == 1 & df1$school_type[i] == 0){
+    df1$treatments[i] <- 1
+
+  }
+  else if (df1$t_mohammad[i] == 0 & df1$school_type[i] == 1){
+    df1$treatments[i] <- 2
+  }
+  else {
[…]

### 2024-02-13 scripts/replication.R
Update replication script for figure 1 in our paper

@@ -134,6 +134,61 @@ ggplot(data, aes(x = group, y = mean, fill = group)) +
        y = "Mean") +
   theme_minimal()
 
+####Estimates used in Panel C
+m1fig3c <- lm_robust(accept1~I(t_mohammad==0), data=df1, se_type="HC2")
+m2fig3c <- lm_robust(accept1~t_mohammad, data=df1, se_type="HC2")
+
+figure3c <- tibble(
+  Treatment = c("Muslim","Danish"),
+  avg = c(coef(m1fig3c)[1],coef(m2fig3c)[1]), 
+  lower = c(confint(m1fig3c)[c(1)],confint(m2fig3c)[c(1)]),
+  upper = c(confint(m1fig3c)[c(3)],confint(m2fig3c)[c(3)])
+)
+
+####Figure in Panel A
+fig3a <-  ggplot(figure3a, aes(x=Treatment,y=avg,fill=Treatment)) +
+  geom_bar(stat="identity",position="dodge", color= "black", width=.5)+
+  geom_errorbar(aes(ymin=lower, ymax=upper), width=.2,position=position_dodge(.9))+
+  geom_text(aes(y=upper, label=round(avg,3)), position=position_dodge(width=0.9), vjust=-.75)+
+  labs(y="Decision Type Rate",x="Clear Rejection",title="A")+
+  scale_fill_manual(values=c("grey","white")) +  
+  scale_y_continuous(breaks=c(0,.1,.2,.3,.4,.5), limits=c(0,.5))+
+  theme_minimal()+
+  theme(text = element_text(size=12),
+        axis.text.x=element_blank(), axis.ticks.x=element_blank()) 
+
+####Figure in Panel B
+fig3b <- ggplot(figure3b, aes(x=Treatment,y=avg,fill=Treatment)) +
+  geom_bar(stat="identity",position="dodge", color= "black", width=.5)+
+  geom_errorbar(aes(ymin=lower, ymax=upper), width=.2,position=position_dodge(.9))+
+  geom_text(aes(y=upper, label=round(avg,3)), position=position_dodge(width=0.9), vjust=-.75)+  
+  labs(y="",x="Unclear Response", title="B")+
+  scale_fill_manual(values=c("grey","white")) +  
+  scale_y_continuous(breaks=c(0,.1,.2,.3,.4,.5), limits=c(0,.5))+
+  theme_minimal()+
+  theme(text = element_text(size=12),legend.position="none",
[…]

### 2024-02-13 scripts/replication.R
update replication script for figure 3 in the original paper

@@ -134,6 +134,7 @@ ggplot(data, aes(x = group, y = mean, fill = group)) +
        y = "Mean") +
   theme_minimal()
 
+### replication for Figure 3 in the original paper ###
 ####Estimates used in Panel C
 m1fig3c <- lm_robust(accept1~I(t_mohammad==0), data=df1, se_type="HC2")
 m2fig3c <- lm_robust(accept1~t_mohammad, data=df1, se_type="HC2")

### 2024-02-13 scripts/04-model.R
Update replicated figure (figure3) in the script

@@ -27,12 +27,12 @@ load("inputs/data/df1.rda")
 ### Graph for proportion of different types of response based on senders'ethnicity and big city ###
 
 # calculation for proportion 
-prop1 <- sum(df1$t_mohammad == '0' & df1$reject1 == '1' & df1$bigcity == '1')/sum(df1$t_mohammad == '0' & df1$bigcity == '1')
-prop2 <-sum(df1$t_mohammad == '1' & df1$reject1 == '1' & df1$bigcity == '1')/sum(df1$t_mohammad == '1' & df1$bigcity == '1')
-prop3 <-sum(df1$t_mohammad == '0' & df1$unclear1 == '1' & df1$bigcity == '1')/sum(df1$t_mohammad == '0' & df1$bigcity == '1')
-prop4 <-sum(df1$t_mohammad == '1' & df1$unclear1 == '1' & df1$bigcity == '1')/sum(df1$t_mohammad == '1' & df1$bigcity == '1')
-prop5 <- sum(df1$t_mohammad == '0' & df1$accept1 == '1' & df1$bigcity == '1')/sum(df1$t_mohammad == '0' & df1$bigcity == '1')
-prop6 <- sum(df1$t_mohammad == '1' & df1$accept1 == '1' & df1$bigcity == '1')/sum(df1$t_mohammad == '1' & df1$bigcity == '1')
+prop1 <- sum(df1$t_mohammad == '1' & df1$reject1 == '1' & df1$bigcity == '1')/sum(df1$t_mohammad == '1' & df1$bigcity == '1')
+prop2 <-sum(df1$t_mohammad == '0' & df1$reject1 == '1' & df1$bigcity == '1')/sum(df1$t_mohammad == '0' & df1$bigcity == '1')
+prop3 <-sum(df1$t_mohammad == '1' & df1$unclear1 == '1' & df1$bigcity == '1')/sum(df1$t_mohammad == '1' & df1$bigcity == '1')
+prop4 <-sum(df1$t_mohammad == '0' & df1$unclear1 == '1' & df1$bigcity == '1')/sum(df1$t_mohammad == '0' & df1$bigcity == '1')
+prop5 <- sum(df1$t_mohammad == '1' & df1$accept1 == '1' & df1$bigcity == '1')/sum(df1$t_mohammad == '1' & df1$bigcity == '1')
[…]

### 2024-02-13 scripts/replication.R

@@ -134,8 +134,37 @@ ggplot(data, aes(x = group, y = mean, fill = group)) +
        y = "Mean") +
   theme_minimal()
 
-### replication for Figure 3 in the original paper ###
+
+##########################################
+#Figure 3: Decision Type Rate by Treatment
+##########################################
+
+####Estimates used in Panel A
+m1fig3a <- lm_robust(reject1~I(t_mohammad==0), data=df1, se_type="HC2")
+m2fig3a <- lm_robust(reject1~t_mohammad, data=df1, se_type="HC2")
+
+figure3a <- tibble(
+  Treatment = c("Muslim","Danish"),
+  avg = c(coef(m1fig3a)[1],coef(m2fig3a)[1]), 
+  lower = c(confint(m1fig3a)[c(1)],confint(m2fig3a)[c(1)]),
+  upper = c(confint(m1fig3a)[c(3)],confint(m2fig3a)[c(3)])
+)
+
+####Estimates used in Panel B
+m1fig3b <- lm_robust(unclear1~I(t_mohammad==0), data=df1, se_type="HC2")
+m2fig3b <- lm_robust(unclear1~t_mohammad, data=df1, se_type="HC2")
+
+figure3b <- tibble(
+  Treatment = c("Muslim","Danish"),
+  avg = c(coef(m1fig3b)[1],coef(m2fig3b)[1]), 
+  lower = c(confint(m1fig3b)[c(1)],confint(m2fig3b)[c(1)]),
+  upper = c(confint(m1fig3b)[c(3)],confint(m2fig3b)[c(3)])
+)
+
 ####Estimates used in Panel C
+m1fig3c <- lm_robust(accept1~I(t_mohammad==0), data=df1, se_type="HC2")
+m2fig3c <- lm_robust(accept1~t_mohammad, data=df1, se_type="HC2")
+
 m1fig3c <- lm_robust(accept1~I(t_mohammad==0), data=df1, se_type="HC2")
 m2fig3c <- lm_robust(accept1~t_mohammad, data=df1, se_type="HC2")
 

### 2024-02-14 outputs/paper/paper.qmd
Update paper (Data section)

@@
 ---
-title: "My title"
+title: "Bureaucratic discrimination stemming from Islamophobia needs to be highlighted"
 subtitle: "My subtitle if needed"
@@
 
-You can and should cross-reference sections and sub-sections.
+From the past to the present, bureaucracy has been a characteristic predominantly found in large companies or public institutions.
+With the nature of bureaucracy, specific individuals or groups within an organization tend to hold the authority to make most administrative decisions, which can result in administrative discrimination stemming from subjective or group opinions or beliefs influencing administrative decisions.
 
-The remainder of this paper is structured as follows. @sec-data.... \newpage
+The original study, “The Unequal Distribution of Opportunity: A National Audit Study of Bureaucratic Discrimination in Primary School Acces (2020) by Olsen, Kyhse-Anderson, Moynihan”, experimented with the unequal opportunities brought about by bureaucratic discrimination in Danish primary schools. Before the experiment, Olsen, Kyhse-Anderson, Moynihan defined bureaucratic discrimination as two forms: either through withholding opportunities in service or imposing administrative burdens to make bureaucratic procedures more complex and difficult. As a result, the original study revealed that individuals with Muslim names experience both forms of bureaucratic discrimination more frequently than those with native (Danish) names.
+
+Our paper will reproduce these findings and will focus on the potential administrative discrimination against Muslims in Canada by building on the two forms of administrative discrimination (1.
+withholding opportunities in service, 2.
+imposing administrative burdens to make bureaucratic procedures more complex and difficult) Through the original experiment’s results, we discovered that administrative discrimination against Muslims could be driven by Islamophobic attitudes.
+Based on the two forms of bureaucratic discrimination defined in the original experiment, our study aims to assess perceptions of Muslims in Canada and discuss the potential for widespread administrative discrimination against Muslims.
+
+\newpage
 
@@
 
-The original paper, "The Unequal Distribution of Opportunity: A National Audit Study of Bureaucratic Discrimination in Primary School Access(2020) by Olsen, Kyhse-Anderson, Moynihan", was replicated from American Journal of Social Science.
+This paper reproduces two results from "The Unequal Distribution of Opportunity: A National Audit Study of Bureaucratic Discrimination in Primary School Access(2020) by Olsen, Kyhse-Anderson, Moyni-han" in the American Journal of Social Science.
+In the original study, the results showed disparities in decision type rates, compliance cost rates, and psychological cost rates. 
+For the decision type, response emails were classified into three categories: clear reject, unclear response, and clear accept.(Examples 1-4 in Appendix A illustrate unclear responses)
+As for compliance cost, it was categorized into four groups based on the format of the email content: simple question, complex question, request a phone call, and request to meet.
+Since decision type rates and compliance cost rates represent two forms of administrative discrimination above, our study will also verify these two sets of results and discuss the potential administrative discrimination against Muslims in Canada.
 
-@fig-decision_rate1 is one of the results in the original study, and it shows the decision type rate based on the different treatments (Muslim/Danish).
-In addition to the results depicted in @fig-decision_rate1, we proceeded the analysis by incorporating new variables, namely the characteristics of schools.
+## Methodology
 
-```{r}
-#| echo: false
-#| label: fig-decision_rate1
-#| message: false
-#| fig-cap: Decision type rate based on each treatment
-knitr::include_graphics(file.path(here::here(),"outputs/models/replicated_figure.png"))
-```
-
-## Overview of Senders and Respondents' traits
-
-In the original experiment, the designed sender attributes consist of two categories: names (Muslim and Danish names) and the Diligence trait.
-Also, the respondent schools are classified based on six characteristics: whether the school is located in a major city, its geographical region, the average student grades, the number of students, the number of non-Danish students, and the school type.
-Theses school characteristics were investigated through the Danish Ministry of Education database in the original study.
-Below is a summary.
+The original experiment was conducted with 1,698 primary schools in Denmark, where fictitious emails regarding student transfer requests were sent to each school.
+These emails were sent under different names (Muslim/Danish), with 850 emails sent under one name and 848 under the other.
+Fictitious students were also assigned diligence traits, which could be discerned from the content of the emails (Overview of Senders’ and Respondents’ traits).
+Additionally, the original study examined both the characteristics of the schools and those of the senders.
+The characteristics of the schools (whether the school is located in a major city, its geographical region, the average student grades, the number of students, the number of non-Danish students, and the school type.) were investigated using the Danish Ministry of Education database, while the characteristics of the senders were determined based on the content of the response emails.
 
@@
 
-## Methodology
-
-As mentioned above, this paper examines how the characteristics of schools, in addition to the original experiment's results for decision type rates, impact Muslim's admission to private schools in Denmark.
-The following subsection will provide detailed explanations of how and why each piece of data was used or not.
-
-### Decision type
-
-As shown on @fig-decision_rate1, in the original study, the schools' responses were categorized into three decision types: clear rejection, unclear response and clear acceptance.
-According to the study, two coders categorized each response email into these three decision types, and the responses categorized by two coders were denoted by response1 and response2.
-As a result, the Cronbach's alpha analysis revealed minimal difference in perception between the two coders regarding the response emails.
-Therefore, in this paper, only Response type 1 is used, and the they are denoted as reject1, unclear1, accept1 in the data set.
-
-### Using Senders and Respondents' traits
-
-Followed by the Senders and Respondents' trait above, the original study also investigated whether each school is above the median level of trait(Number of Students, Number of Non-Danish Students and Students' grade).
-Based on this examination, this study examined how schools with above-median and below-median traits influence the decision type rate through proportional contrasts.
-Additionally, the impact of school location and school type on Muslim's decision type rate will be investigated.
-
-### Not using Diligence trait
-
-Finally, diligence trait is excluded from this study.
-This decision is based on the original research, which revealed through the full ordinary least square(OLS) results that diligence traits do not have any effect on outcome variables such as response rate or the decision to accept or reject students.
+### Effect of Senders and Respondents' trait
+Lastly, the original study revealed through the full ordinary least squares (OLS) results that neither the diligence trait nor the characteristics of schools have any influence on the outcome variables (decision type, compliance cost).
+Consequently, apart from racial characteristics based on two different names, no other traits will be mentioned in this paper.
 

### 2024-02-14 outputs/paper/paper.qmd
Update paper(Data section)

@@
 
-The original study, “The Unequal Distribution of Opportunity: A National Audit Study of Bureaucratic Discrimination in Primary School Acces (2020) by Olsen, Kyhse-Anderson, Moynihan”, experimented with the unequal opportunities brought about by bureaucratic discrimination in Danish primary schools. Before the experiment, Olsen, Kyhse-Anderson, Moynihan defined bureaucratic discrimination as two forms: either through withholding opportunities in service or imposing administrative burdens to make bureaucratic procedures more complex and difficult. As a result, the original study revealed that individuals with Muslim names experience both forms of bureaucratic discrimination more frequently than those with native (Danish) names.
+The original study, “The Unequal Distribution of Opportunity: A National Audit Study of Bureaucratic Discrimination in Primary School Acces (2020) by Olsen, Kyhse-Anderson, Moynihan”, experimented with the unequal opportunities brought about by bureaucratic discrimination in Danish primary schools.Before the experiment, Olsen, Kyhse-Anderson, Moynihan defined bureaucratic discrimination as two forms: either through withholding opportunities in service or imposing administrative burdens to make bureaucratic procedures more complex and difficult.
+As a result, the original study revealed that individuals with Muslim names experience both forms of bureaucratic discrimination more frequently than those with native (Danish) names.
 
@@
 withholding opportunities in service, 2.
-imposing administrative burdens to make bureaucratic procedures more complex and difficult) Through the original experiment’s results, we discovered that administrative discrimination against Muslims could be driven by Islamophobic attitudes.
+imposing administrative burdens to make bureaucratic procedures more complex and difficult).
+Through the original experiment’s results, we discovered that administrative discrimination against Muslims could be driven by Islamophobic attitudes.
 Based on the two forms of bureaucratic discrimination defined in the original experiment, our study aims to assess perceptions of Muslims in Canada and discuss the potential for widespread administrative discrimination against Muslims.
@@
 This paper reproduces two results from "The Unequal Distribution of Opportunity: A National Audit Study of Bureaucratic Discrimination in Primary School Access(2020) by Olsen, Kyhse-Anderson, Moyni-han" in the American Journal of Social Science.
-In the original study, the results showed disparities in decision type rates, compliance cost rates, and psychological cost rates. 
+In the original study, the results showed disparities in decision type rates, compliance cost rates, and psychological cost rates between Muslim and Danish. 
 For the decision type, response emails were classified into three categories: clear reject, unclear response, and clear accept.(Examples 1-4 in Appendix A illustrate unclear responses)
-As for compliance cost, it was categorized into four groups based on the format of the email content: simple question, complex question, request a phone call, and request to meet.
-Since decision type rates and compliance cost rates represent two forms of administrative discrimination above, our study will also verify these two sets of results and discuss the potential administrative discrimination against Muslims in Canada.
+Also, for compliance cost, it was categorized into four groups based on the format of the email content: simple question, complex question, request a phone call, and request to meet.
+Since the difference of decision type rates and compliance cost rates between Danish and Muslim represent two forms of administrative discrimination mentioned above, our study will also verify these two sets of results and discuss the potential administrative discrimination against Muslims in Canada.
 

### 2024-02-14 inputs/data/ms_tables_figures.R
fixed a pathing issue in replication package

@@ -36,7 +36,7 @@ library(grid)
 setwd(dirname(rstudioapi::getSourceEditorContext()$path))
 
 #load data for main analysis
-load("inputs/data/df1.rda")
+load("df1.rda")
 
 ##########################################################
 # Facts in section 'Abstract' & 'Introduction'

### 2024-02-14 scripts/04-model.R
Update results

@@ -9,304 +9,23 @@
 # it is recommended to read the codebook and df1.rda file to acknowledge variables used in the below script
 
 #### Workspace setup ####
-install.packages("gridExtra")
-install.packages("texreg")
-install.packages("scales")
-install.packages("cowplot")
+install.packages("webshot2")
+install.packages("flextable")
+library(kableExtra)
+library(webshot2)
+library(flextable)
 
-library(tidyverse)
-library(ggplot2)
-library(gridExtra)
-library(texreg)
-library(scales)
-library(cowplot)
-library(data.table)
+### Table 1: 10 Examples of response emails ###
+Table1 <- tibble("Examples of 10 Responses from the Schools" = c("Hello <first name>. I would like to know a little more about your son. Where does he live and what school does he go to? Once I have received this information, I will bring it to a manager. Good day. Sincerely <sender>",
+                                                                 "Hi <first name>. Thanks for your mail. Before I can answer you if we have room, I need to know your address so we can check if you live in our school district... Sincerely <sender>",
+                                                                 "Dear <first name> <surname> . Thank you for your mail with inquiry about a possible school transfer. Where do you live? Where is your son at school now? What is the reason you want a school transfer? You are welcome to contact me at <phone number> or <phone number>, so we can talk more about any visit to <school name>... Sincerely <sender>",
+                                                                 "Hello <first name>. Thank you for your email concerning a school transfer for your son, and I need to have an in-depth chat with you to get a closer look at the problem. Can you call me at either mobile: <phone number> or my extension: <phone number>. Sincerely <sender>",
+                                                                 "Hi <firstname> Unfortunately, there is no room on <schoolname> in 3rd grade unless you live in the school district. <sender>",
[…]

### 2024-02-14 scripts/replication.R

@@ -181,7 +181,6 @@ figure3c <- tibble(
 ####Figure in Panel A
 fig3a <-  ggplot(figure3a, aes(x=Treatment,y=avg,fill=Treatment)) +
   geom_bar(stat="identity",position="dodge", color= "black", width=.5)+
-  geom_errorbar(aes(ymin=lower, ymax=upper), width=.2,position=position_dodge(.9))+
   geom_text(aes(y=upper, label=round(avg,3)), position=position_dodge(width=0.9), vjust=-.75)+
   labs(y="Decision Type Rate",x="Clear Rejection",title="A")+
   scale_fill_manual(values=c("grey","white")) +  
@@ -193,7 +192,6 @@ fig3a <-  ggplot(figure3a, aes(x=Treatment,y=avg,fill=Treatment)) +
 ####Figure in Panel B
 fig3b <- ggplot(figure3b, aes(x=Treatment,y=avg,fill=Treatment)) +
   geom_bar(stat="identity",position="dodge", color= "black", width=.5)+
-  geom_errorbar(aes(ymin=lower, ymax=upper), width=.2,position=position_dodge(.9))+
   geom_text(aes(y=upper, label=round(avg,3)), position=position_dodge(width=0.9), vjust=-.75)+  
   labs(y="",x="Unclear Response", title="B")+
   scale_fill_manual(values=c("grey","white")) +  
@@ -205,7 +203,6 @@ fig3b <- ggplot(figure3b, aes(x=Treatment,y=avg,fill=Treatment)) +
 ####Figure in Panel C
 fig3c <- ggplot(figure3c, aes(x=Treatment,y=avg,fill=Treatment)) +
   geom_bar(stat="identity",position="dodge", color= "black", width=.5)+
-  geom_errorbar(aes(ymin=lower, ymax=upper), width=.2,position=position_dodge(.9))+
   geom_text(aes(y=upper, label=round(avg,3)), position=position_dodge(width=0.9), vjust=-.75)+  
   labs(y="",x="Clear Acceptance",title="C")+
   scale_fill_manual(values=c("grey","white")) + 
@@ -223,7 +220,101 @@ fig3 <- grid.arrange(fig3a, fig3b, fig3c, legend, nrow = 1, widths=c(2, 2, 2, 1)
 ggsave(file = "replicated_figure.png",fig3,path = "outputs/models",width=8,height=4,scale=1)
 
 
[…]

### 2024-02-14 outputs/paper/paper.qmd

@@
 title: "Bureaucratic discrimination stemming from Islamophobia needs to be highlighted"
-subtitle: "My subtitle if needed"
 author: 
@@
   - Another author
-thanks: "Code and data are available at: LINK."
+thanks: "Code and data are available at: https://github.com/SachinChhikara/administrative_discrimination_analysis.git"
 date: today
@@
 format: pdf
+toc: true
 number-sections: true
@@
 library(tidyverse)
-library(palmerpenguins)
+library(knitr)
+library(flextable)
 ```
@@
 
-Our paper will reproduce these findings and will focus on the potential administrative discrimination against Muslims in Canada by building on the two forms of administrative discrimination (1.
-withholding opportunities in service, 2.
-imposing administrative burdens to make bureaucratic procedures more complex and difficult).
+Our paper will reproduce these findings and will focus on the potential administrative discrimination against Muslims in Canada by building on the two forms of administrative discrimination (1.Withholding opportunities in service, 2.Imposing administrative burdens to make bureaucratic procedures more complex and difficult).
 Through the original experiment’s results, we discovered that administrative discrimination against Muslims could be driven by Islamophobic attitudes.
-Based on the two forms of bureaucratic discrimination defined in the original experiment, our study aims to assess perceptions of Muslims in Canada and discuss the potential for widespread administrative discrimination against Muslims.
-
-\newpage
+Based on the two forms of bureaucratic discrimination defined in the original experiment, our study aims to assess perceptions about Muslims in Canada and discuss the potential for widespread administrative discrimination against Muslims.
 
@@
 
-This paper reproduces two results from "The Unequal Distribution of Opportunity: A National Audit Study of Bureaucratic Discrimination in Primary School Access(2020) by Olsen, Kyhse-Anderson, Moyni-han" in the American Journal of Social Science.
+This paper reproduces two results from "The Unequal Distribution of Opportunity: A National Audit Study of Bureaucratic Discrimination in Primary School Access(2020) by Olsen, Kyhse-Anderson, Moynihan" in the American Journal of Social Science.
+Our study mainly focuses on the findings whether 1) Muslim gets withdrawn from the public service more frequently 2) Muslims gets the the administrative burdens more often than Danish.
 In the original study, the results showed disparities in decision type rates, compliance cost rates, and psychological cost rates between Muslim and Danish.
-For the decision type, response emails were classified into three categories: clear reject, unclear response, and clear accept.(Examples 1-4 in Appendix A illustrate unclear responses)
+For the decision type, response emails were classified into three categories: clear reject, unclear response, and clear accept.
 Also, for compliance cost, it was categorized into four groups based on the format of the email content: simple question, complex question, request a phone call, and request to meet.
@@
 The characteristics of the schools (whether the school is located in a major city, its geographical region, the average student grades, the number of students, the number of non-Danish students, and the school type.) were investigated using the Danish Ministry of Education database, while the characteristics of the senders were determined based on the content of the response emails.
+
+### Senders and Respondents'(schools) trait
 
@@
 
+### Measurement for administrative discrimination
+
+-   ***Type of Administrative Discrimination***
+
+    -   [**Withdrawing Opportunity**]{.underline}
+
+        Categorizing receiving emails by 3 categories
+
+        1.  Clear Reject
+        2.  Unclear Response
+        3.  Clear Acceptance
+
+        [**Giving administrative burdens**]{.underline}
+
+        Categorizing receiving emails by 4 categories
+
+        1.  Simple Question
+        2.  Complex Question
+        3.  Request a Phone call
+        4.  Request to meet
+
 ### Effect of Senders and Respondents' trait
+
 Lastly, the original study revealed through the full ordinary least squares (OLS) results that neither the diligence trait nor the characteristics of schools have any influence on the outcome variables (decision type, compliance cost).
@@
 
+\newpage
 # Results
 
-Our results are summarized in @tbl-modelresults.
+## Decision type rate
+
+```{r}
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+#| label: fig-decision_type
+#| fig-cap: "Decision type rate based on each treatment"
+knitr::include_graphics(file.path(here::here(),"outputs/models/replicated_figure.png")) 
+```
+
+@fig-decision_type illustrates the decision type rate of schools based on two ethnic groups (Danish/Muslim).
+As evident from the figures, Muslims received approximately 7.4% more clear admission rejections compared to Danes, and unclear responses were also approximately 2.4% higher for Muslims.
+In contrast, for clear admission acceptance, Danes were approximately 9.8% higher.
+The higher rate of clear rejections for Muslims compared to Danes demonstrates one form of administrative discrimination, where individuals are initially deprived of opportunities.
+Conversely, the higher rate of clear admission approvals for Danes compared to Muslims also signifies receiving fewer opportunities in education, a public service, indicating exclusion of Muslims as recipients of public service opportunities due to the first form of administrative discrimination.
+
+## Compliance Cost rate
+
+```{r}
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+#| label: fig-compliance_cost
+#| fig-cap: "Compliance cost rate based on each treatment"
+knitr::include_graphics(file.path(here::here(),"outputs/models/replicated_figure2.png")) 
+```
+
+@fig-compliance_cost displays the compliance cost rate between each ethnic group.
+Muslims showed higher frequencies in both simple and complex questions, with 8.5% and 0.5% more, respectively.
+This indicates that Muslims are subjected to discrimination in the form of imposing administrative burdens.
+Regarding the request for meetings, there was not a significant difference between the two racial groups.
+However, in contrast to simple and complex questions, Danish individuals showed a 14% higher rate of requesting phone calls.
+According to the interpretation of the original study results, administrative officers responsible for admissions utilized phone calls as an informal verification method, indicating higher social trust towards Danes.
+Therefore, the higher rate of phone call requests for Danes does not represent compliance costs but rather reflects higher social trust towards Danes, highlighting administrative discrimination against Muslims.
 
@@
 
-## First discussion point {#sec-first-point}
+## Perception about Muslims in Canada and Potential Administrative Discrimination againt them  {#sec-first-point}
 
@@
 
-## Second discussion point
-
-## Third discussion point
+## Ethical Reflection
+aaa
 
@@
 # References
+
+---
+nocite: '@*'
+---

### 2024-02-15 outputs/paper/paper.qmd
Update Data section

@@
 author: 
-  - First author
-  - Another author
+  - Fares Alkorani
+  - Kyungrok Park 
+  - Sachin Chihikara
 thanks: "Code and data are available at: https://github.com/SachinChhikara/administrative_discrimination_analysis.git"
@@
 library(knitr)
-library(flextable)
 ```
@@
 
-The original study, “The Unequal Distribution of Opportunity: A National Audit Study of Bureaucratic Discrimination in Primary School Acces (2020) by Olsen, Kyhse-Anderson, Moynihan”, experimented with the unequal opportunities brought about by bureaucratic discrimination in Danish primary schools.Before the experiment, Olsen, Kyhse-Anderson, Moynihan defined bureaucratic discrimination as two forms: either through withholding opportunities in service or imposing administrative burdens to make bureaucratic procedures more complex and difficult.
+The original study, “The Unequal Distribution of Opportunity: A National Audit Study of Bureaucratic Discrimination in Primary School Acces (2020) by Olsen, Kyhse-Anderson, Moynihan”, experimented with the unequal opportunities brought about by bureaucratic discrimination in Danish primary schools.
+Before the experiment, Olsen, Kyhse-Anderson, Moynihan defined bureaucratic discrimination as two forms: either through withholding opportunities in service or imposing administrative burdens to make bureaucratic procedures more complex and difficult.
 As a result, the original study revealed that individuals with Muslim names experience both forms of bureaucratic discrimination more frequently than those with native (Danish) names.
@@
 Our paper will reproduce these findings and will focus on the potential administrative discrimination against Muslims in Canada by building on the two forms of administrative discrimination (1.Withholding opportunities in service, 2.Imposing administrative burdens to make bureaucratic procedures more complex and difficult).
+Thus, the estimand for our research will be the effect of being Muslims to get admitted to the private school in Denmark (Broadly effect of being Muslims to access the public service) . 
 Through the original experiment’s results, we discovered that administrative discrimination against Muslims could be driven by Islamophobic attitudes.
 Based on the two forms of bureaucratic discrimination defined in the original experiment, our study aims to assess perceptions about Muslims in Canada and discuss the potential for widespread administrative discrimination against Muslims.
+In our study, the statistical programming language R software (R Core Team, 2023) was used for replication purposes.
+Additional packages, tidyverse (Wickham et al.2019), knitr(Xie 2014), ltm(Rizopoulos 2006), grindExtra(Auguie 2017), estimatr, texreg(Leifeld 2013), scales(Wickham et al.
+2023), cowplot(O.
+Wilke 2024), ggplot2 (Wickham 2016) and here(Müller 2020) were also utilized for our further analysis and reproduction.
+
+This paper is organized into 4 sections: Introduction, Data, Results and Discussion.
+The Data section provides a description of the variables and experimental setup used in the original paper, including how administrative discrimination was measured.
+The Results section cites two graphs from the original paper to reaffirm the existence of administrative discrimination against Muslims in Denmark.
+Finally, in the Discussion section, it is asserted that such administrative discrimination may occur or is occurring in Canada, leveraging Islamophobic sentiments or perceptions of Muslims.
 
@@
 Our study mainly focuses on the findings whether 1) Muslim gets withdrawn from the public service more frequently 2) Muslims gets the the administrative burdens more often than Danish.
-In the original study, the results showed disparities in decision type rates, compliance cost rates, and psychological cost rates between Muslim and Danish.
-For the decision type, response emails were classified into three categories: clear reject, unclear response, and clear accept.
-Also, for compliance cost, it was categorized into four groups based on the format of the email content: simple question, complex question, request a phone call, and request to meet.
-Since the difference of decision type rates and compliance cost rates between Danish and Muslim represent two forms of administrative discrimination mentioned above, our study will also verify these two sets of results and discuss the potential administrative discrimination against Muslims in Canada.
 
@@
 The characteristics of the schools (whether the school is located in a major city, its geographical region, the average student grades, the number of students, the number of non-Danish students, and the school type.) were investigated using the Danish Ministry of Education database, while the characteristics of the senders were determined based on the content of the response emails.
+Furthermore, email responses to transfer requests received from schools were measured in terms of decision type rate, compliance cost rate, and psychological cost rate for each ethnicity (Danish/Muslim), depending on the content of the email.
+For the decision type, response emails were classified into three categories: clear reject, unclear response, and clear accept.
+Also, for compliance cost, it was categorized into four groups based on the format of the email content: simple question, complex question, request a phone call, and request to meet.
+Since the difference of decision type rates and compliance cost rates between Danish and Muslim represent two forms of administrative discrimination mentioned above, our study will also verify these two sets of results and discuss the potential administrative discrimination against Muslims in Canada.
 
@@
 
-\newpage
 # Results

### 2024-02-15 inputs/data/ms_tables_figures.R
Remove files

@@ -1,736 +1,0 @@
-# ########################################################################################
-#
-# Code: October 7, 2020
-# 
-# Title: The Unequal Distribution of Opportunity: 
-# A National Audit Study of Bureaucratic Discrimination in Primary School Access
-#
-# Authors: Asmus Leth Olsen, Jonas H?gh Kyhse-Andersen and Donald Moynihan                                                                          
-#                                   
-# Summary: Replication code for producing all tables, figures and facts in the main text.    
-#
-# Please report errors to: Asmus Leth Olsen, at: ajlo@ifs.ku.dk
-#
-# #########################################################################################
-
-rm(list = ls())
-
-#load packages
-library(tidyverse)
-library(ltm)
-library(gridExtra)
-library(estimatr)
-library(texreg)
-library(scales)
-library(cowplot)
-library(grid)
-
-####################
-# Note to the reader
-####################
-
-# This script is arranged in the order as the figures, tables and facts are presented in the manuscript.
-# A separate codebook provides definition of all variables and their respective values.
-
-##set path for data
-setwd(dirname(rstudioapi::getSourceEditorContext()$path))
-
-#load data for main analysis
-load("df1.rda")
-
-##########################################################
-# Facts in section 'Abstract' & 'Introduction'
-##########################################################
-
-#N in the main data file
-nrow(df1)
-
-#Main finding: difference of ~10 percentage point in acceptance for the main treatment
-main<-lm_robust(accept1~t_mohammad, data=df1, se_type="HC2")
-summary(main)
-
-#acceptance rate for Danish treatment in percent
-round(coef(main)[1]*100,1)
-
-#acceptance rate for Muslim treatment in percent
-round(coef(main)[1]*100,1)+round(coef(main)[2]*100,1)
-
-##########################################################################################
-# Figure 1: Total Number of Students and Percentage of Non-native Danish Students in Each 
-##########################################################################################
-
-#load data for descriptives on schools
-load("school_df.Rda")
-
[…]

### 2024-02-15 inputs/data/si_tables_figures.R

@@ -1,628 +1,0 @@
-# ########################################################################################
-#
-# Code: October 7, 2020
-# 
-# Title: The Unequal Distribution of Opportunity: 
-# A National Audit Study of Bureaucratic Discrimination in Primary School Access
-#
-# Authors: Asmus Leth Olsen, Jonas Høgh Kyhse-Andersen and Donald Moynihan                                                                           
-#                                   
-# Summary: Replication code for Supporting Information. 
-#
-# Please report errors to: Asmus Leth Olsen, at: ajlo@ifs.ku.dk
-#
-# #########################################################################################
-
-###
-rm(list = ls())
-
-#load packages
-library(estimatr)
-library(MASS)
-library(nnet)
-library(texreg)
-library(tidyverse)
-
-####################
-# Note to the reader
-####################
-
-# This script is arranged in the order as the figures and tables in the Supporting Information
-# A separate codebook provides definition of all variables and their respective values.
-
-##set path for data
-setwd(dirname(rstudioapi::getSourceEditorContext()$path))
-
-#load data df1
-load("df1.Rda")
-
-##########################################################################################################
-# SI A -- Administrative Burdens and Existing Audit Studies 
-##########################################################################################################
-
-#SI A does not rely on data from this file.
-
-####################################################################################
-# SI -- B: Share of Non-Western Immigrants and School Grade Average
-####################################################################################
-
-#load data for descriptives on schools
-load("school_df.Rda")
-
-m1 <- lm_robust(avg_grades~pct_non_danes, data=school_df, se_type="HC2")
-
-htmlreg(
-  m1,
-  file = "tableB1.doc",
-  custom.coef.names = c(
-    "Intercept",
-    "Pct Non-Danish"),
-  reorder.coef = c(2,1),
-  custom.model.names = c("1"),
[…]

### 2024-02-15 outputs/paper/paper.qmd
Update references

@@
 This paper reproduces two results from "The Unequal Distribution of Opportunity: A National Audit Study of Bureaucratic Discrimination in Primary School Access(2020) by Olsen, Kyhse-Anderson, Moynihan" in the American Journal of Social Science.
-Our study mainly focuses on the findings whether 1) Muslim gets withdrawn from the public service more frequently 2) Muslims gets the the administrative burdens more often than Danish.
+Our study mainly focuses on the findings whether 1) Muslim gets withdrawn from the public service more frequently 2) Muslims gets the administrative burdens more often than Danish.
 
@@
 Also, for compliance cost, it was categorized into four groups based on the format of the email content: simple question, complex question, request a phone call, and request to meet.
-Since the difference of decision type rates and compliance cost rates between Danish and Muslim represent two forms of administrative discrimination mentioned above, our study will also verify these two sets of results and discuss the potential administrative discrimination against Muslims in Canada.
+Since the difference of decision type rates and compliance cost rates between Danish and Muslim represent two forms of administrative discrimination mentioned above, our study will verify these two sets of results and discuss the potential administrative discrimination against Muslims in Canada.
 
@@
 
-        1.  Clear Reject
-        2.  Unclear Response
+        1.  Clear Rejection
+        2.  Unclear Response: captures a absence of any reference to rejection or approval 
         3.  Clear Acceptance
@@
 
-        1.  Simple Question
-        2.  Complex Question
+        1.  Simple Question: captures questions about the name of the child and other basic factual matters
+        2.  Complex Question: captures quetions more detailed information about the child than just basic factual matters
         3.  Request a Phone call
@@
 This indicates that Muslims are subjected to discrimination in the form of imposing administrative burdens.
-Regarding the request for meetings, there was not a significant difference between the two racial groups.
+Regarding the request for meetings, there was not a significant difference between the two ethnic groups.
 However, in contrast to simple and complex questions, Danish individuals showed a 14% higher rate of requesting phone calls.

### 2024-02-15 scripts/01-download_data.R
Remove files

@@ -1,17 +1,0 @@
-#### Preamble ####
-# Purpose: Downloads and saves the data from Harvard's dataverse 
-# Author: Fares Alkorani
-# Date: 11 February 2024
-# Contact: 156137245+faralk@users.noreply.github.com
-# License: MIT
-# Pre-requisites: -
-
-#### Download data ####
-
-# Unfortunately, the data cannot be downloaded automatically.
-# Thus, you can take the following the steps to download the data.
-# 1) First, visit https://dataverse.harvard.edu/dataset.xhtml?persistentId=doi:10.7910/DVN/BFEBHQ.
-# 2) Then, press the 'Access Dataset' button.
-# 3) Press "Download ZIP (384.2 KB).
-
-         

### 2024-02-15 scripts/04-model.R

@@ -1,31 +1,0 @@
-#### Preamble ####
-# Purpose: Models the bar graph for different proportion depending on senders' name and school's traits
-# Author: Kyungrok Park
-# Date: 11 February 2024 
-# Contact: kyungrok.park@mail.utoronto.ca
-# License: MIT
-# Pre-requisites: follow the workspace setup to install and load the following packages
-# Any other information needed? df1.rda file was examined and the graphs were made based on the information in df1.rda, 
-# it is recommended to read the codebook and df1.rda file to acknowledge variables used in the below script
-
-#### Workspace setup ####
-install.packages("webshot2")
-install.packages("flextable")
-library(kableExtra)
-library(webshot2)
-library(flextable)
-
-### Table 1: 10 Examples of response emails ###
-Table1 <- tibble("Examples of 10 Responses from the Schools" = c("Hello <first name>. I would like to know a little more about your son. Where does he live and what school does he go to? Once I have received this information, I will bring it to a manager. Good day. Sincerely <sender>",
-                                                                 "Hi <first name>. Thanks for your mail. Before I can answer you if we have room, I need to know your address so we can check if you live in our school district... Sincerely <sender>",
-                                                                 "Dear <first name> <surname> . Thank you for your mail with inquiry about a possible school transfer. Where do you live? Where is your son at school now? What is the reason you want a school transfer? You are welcome to contact me at <phone number> or <phone number>, so we can talk more about any visit to <school name>... Sincerely <sender>",
-                                                                 "Hello <first name>. Thank you for your email concerning a school transfer for your son, and I need to have an in-depth chat with you to get a closer look at the problem. Can you call me at either mobile: <phone number> or my extension: <phone number>. Sincerely <sender>",
-                                                                 "Hi <firstname> Unfortunately, there is no room on <schoolname> in 3rd grade unless you live in the school district. <sender>",
-                                                                 "Dear <firstname> Unfortunately, we are fully booked in the year group. So, we are not in a position to take in your son. Kind regards <sender>",
-                                                                 "Dear <firstname> <lastname> Unfortunately, we do not have any more places in 3rd grade. You can find information about the school on <website>. Kind regards <sender>",
-                                                                 "Good morning <firstname> Your son is welcome at <schoolname> and it would be fine to hold a meeting, so you can see the school, meet the teachers and we can match our expectations. Would you please contact me – so we can set a date and time? Kind regards <sender>",
[…]

### 2024-02-15 scripts/02-test_data.R
Uploaded test_data and reuploaded download_data

@@ -1,0 +1,51 @@
+#### Preamble ####
+# Purpose: Tests the data given in the df1.rda file
+# Author: Fares Alkorani
+# Date: 15 February 2024
+# Contact: 156137245+faralk@users.noreply.github.com
+# License: MIT
+# Pre-requisites: -
+
+
+#### Workspace setup ####
+library(tidyverse)
+library(dplyr)
+
+#### Test data ####
+
+set.seed(123)
+
+load('inputs/data/df1.rda')
+
+# Confirms if respond date is always after the send date
+
+ifelse(!is.na(df1$send_date) & !is.na(df1$resp_date), (df1$send_date <= df1$resp_date) == TRUE, TRUE)
+class(df1$send_date) == "Date"
+
+# Confirms if the variables are binary
+
+df1$t_mohammad |> unique() == c(0, 1)
+df1$t_good |> unique() == c(0, 1)
+df1$reject1 |> unique() == c(0, 1)
+df1$unclear1 |> unique() == c(1, 0)
+df1$accept1 |> unique() == c(0, 1)
+df1$simple_q |> unique() == c(0, 1)
+df1$simple_q_alt |> unique() == c(0, 1)
+df1$complex_q |> unique() == c(0, 1)
+df1$contact_q |> unique() == c(1, 0)
+df1$meeting_q |> unique() == c(1, 0)
+df1$no_greet |> unique() == c(0, 1)
+df1$greet_no_name |> unique() == c(0, 1)
+df1$informal_greet |> unique() == c(1, 0)
+df1$formal_greet |> unique() == c(0, 1)
+
+
+# Checks for if every row, there are two different columns
+
+all(df1$reject1 != df1$unclear1 | df1$accept1)
+all(df1$unclear1 != df1$accept1 | df1$reject1)
+all(df1$accept1 != df1$unclear1 | df1$reject1)
+
+
+
+

### 2024-02-15 outputs/paper/paper.qmd
Update discussion

@@
 
-If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.
+Canada is not new to Islamophobic attitudes and so, it is worth exploring the results of this study and their implications with respect to Canada, especially Quebec.
+
+Bill 21, a bill passed in Quebec, bars public school teachers, police officers, judges and government lawyers, among other civil servants in positions of authority, from wearing religious symbols — such as hijab, crucifixes or turbans — while at work.
+According to CBC news, this bill has negatively impacted Muslim women the most.
+The article goes to state that a Muslim teacher lost her job for not following this rule and law which tend further hatred towards Muslims.
+Muslim women have experience insults such as "dirty immigrants", "These Muslim women with rags on their heads, if they are not able to integrate, let them return to their country".
+Furthermore, CBC reports that 47% of Muslim women reported to treated unfairly by a person in authority.
+(Rukavina 2022)
+More generally, the general perception towards Muslims in Canada is not favorable as shown in a study conducted by Angus Reid Institute, revealing that 52% of Quebec and 39% rest of Canada view the religion of Islam in an unfavorable manner.
+This study proceeds to suggest that there some correlation between age and education when comes to the discrimination.
+Those who very negatively view of Muslims tend to be more older and half of them have high school diploma or less.
+In contrast, younger Canadians tend to have a very positive view towards Muslims and those who have a post-secondary education.
+Since, in 2005, it was revealed that 57% of Canadian school principals were over the age of 50 years of age or older (Blouin 2005) and by the Canadian Education Act, "each school principal has the drastic power to refuse to admit to school any person whose presence in the school or classroom would in the principal's judgment be detrimental to the physical or mental well-being of the pupils" (AODA 2020), it is unsurprising to imagine how many Canadian Muslim pupils may have been rejected admission from a school strictly on the basis of their religion, in a similar fashion to the Muslim Danish pupils studied in this paper.
+Furthermore, it can be interpreted in a broader sense beyond just school admissions issues, suggesting that administrative discrimination stemming from Islamophobic sentiments could occur when Muslims seek access to various other public services or opportunities.
+However, more research is needed to assess the unequal opportunities faced by Muslims in Canadian schools and other public services resulting from administrative discrimination.
 

### 2024-02-15 outputs/paper/paper.qmd
Updated references and discussion

@@
 
-This paper reproduces two results from "The Unequal Distribution of Opportunity: A National Audit Study of Bureaucratic Discrimination in Primary School Access(2020) by Olsen, Kyhse-Anderson, Moynihan" in the American Journal of Social Science.
+This paper reproduces two results from "The Unequal Distribution of Opportunity: A National Audit Study of Bureaucratic Discrimination in Primary School Access (2020) by Olsen, Kyhse-Anderson, Moynihan" in the American Journal of Social Science.
 Our study mainly focuses on the findings whether 1) Muslim gets withdrawn from the public service more frequently 2) Muslims gets the administrative burdens more often than Danish.
@@
 
-## Perception about Muslims in Canada and Potential Administrative Discrimination againt them  {#sec-first-point}
+## Perception about Muslims in Canada and Potential Administrative Discrimination against Them  {#sec-first-point}
 
@@
 (Rukavina 2022)
+
 More generally, the general perception towards Muslims in Canada is not favorable as shown in a study conducted by Angus Reid Institute, revealing that 52% of Quebec and 39% rest of Canada view the religion of Islam in an unfavorable manner.
@@
 ## Ethical Reflection
-aaa
 
-## Weaknesses and next steps
+In this paper, Olsen, Kyhse-Andersen, and Moynihan discuss the ethical significance of field experiments.
+However, they noted that they must proceed with this study given the policy importance that comes with understanding the barriers to school transfer for Muslim pupils in the Danish schools (CITATION).
+In addition, to minimize risk, the authors anonymized individual responses in the replication data and communicated the results of the study to the Danish school administrators and relevant parties.
 
-Weaknesses and next steps should also be included.
+## Limitations
+
+First, as stated in the original paper, 'the interaction with bureaucrats was limited to an initial response', meaning that it is unknown whether the bureaucrats would have accepted or declined a student in the unclear response case (CITATION).
+While the authors believe the evidence they have lends little support to this possibility, it may significantly skew the distribution of clear acceptances and clear rejections to communicate more substantiated findings.
+
+Second, there were more variables documented with respect to each email that was sent to a school, but were delinked with respect to the original email that was sent to a school to be compliant with GDPR in a Danish context (CITATION).
+These variables included information about the email responder (gender, administrative status, whether they are Muslim or Danish) and information regarding the school (number of students enrolled, average grades of students enrolled, and the proportion of non-Danish students in the school).
+With this information being linked to the data set, more thorough analysis could have been conducted to unravel hidden trends in the discrimination with respect to Muslim admission in Denmark public schools.
+
+## Future Research
+
+First, where possible, this experiment can be reconducted with Canadian public schools to analyze the Canada-specific discrimination to Muslims.
+Secondly, it is worth conducting this experiment in other types of schooling such as in secondary and post-secondary institutions, to analyze whether Muslim discrimination differs across other academic settings.
+Lastly, it may help to add more dimension to this student by incorporating their gender and social class within emails sent out to schools, as this may bring light to more hidden trends and the discrimination that is encountered by specific groups of Muslims.
 

### 2024-02-15 outputs/paper/paper.qmd
Changes to paper and references

@@
 ---
-title: "Bureaucratic discrimination stemming from Islamophobia needs to be highlighted"
+title: "Muslims face more administrative burdens than Danes: Bureaucratic discrimination stemming from Islamophobia needs to be highlighted"
 author: 
@@
   - Sachin Chihikara
-thanks: "Code and data are available at: https://github.com/SachinChhikara/administrative_discrimination_analysis.git"
+thanks: "Code and data are available at: https://github.com/SachinChhikara/administrative_discrimination_analysis.git; Replication on Social Science Reproductions platform is available at: https://doi.org/10.48152/ssrp-ep28-1y61."
 date: today
 date-format: long
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
+abstract: "Bureaucratic discrimination is an ongoing problem on a global scale where people in power engage in discrimination for various reasons.
+This paper analyzes administrative discrimination and burdening faced by Muslim pupils interested in enrolling in a public school by emailing the school under a Muslim and Danish name and noting differences in the responses by administrative staff.
+We find that Muslims face more burdens than Danes and do not receive a clear acceptance into the school as often as the Danes.
+From these findings, further research should be aimed at minimizing administrative discrimination against Muslims not only in school admissions but also in other areas of public services."
 format: pdf
@@
 From the past to the present, bureaucracy has been a characteristic predominantly found in large companies or public institutions.
-With the nature of bureaucracy, specific individuals or groups within an organization tend to hold the authority to make most administrative decisions, which can result in administrative discrimination stemming from subjective or group opinions or beliefs influencing administrative decisions.
+With the nature of bureaucracy, specific individuals or groups within an organization tend to hold the authority to make most administrative decisions, which can result in administrative discrimination stemming from group opinions or beliefs influencing administrative decisions.
 
@@
 
-Our paper will reproduce these findings and will focus on the potential administrative discrimination against Muslims in Canada by building on the two forms of administrative discrimination (1.Withholding opportunities in service, 2.Imposing administrative burdens to make bureaucratic procedures more complex and difficult).
-Thus, the estimand for our research will be the effect of being Muslims to get admitted to the private school in Denmark (Broadly effect of being Muslims to access the public service) . 
-Through the original experiment’s results, we discovered that administrative discrimination against Muslims could be driven by Islamophobic attitudes.
+Our paper will reproduce these findings and will focus on the potential administrative discrimination against Muslims in Canada by building on the two forms of administrative discrimination.
+This includes 1) withholding opportunities in service and 2) imposing administrative burdens to make bureaucratic procedures more complex and difficult.
+Thus, the estimand for our research will be measuring the effect of being Muslim to receiving admission to the primary school in Denmark (broad effect would be analyzing the degree to which Muslims can access public services).
+Through the results of the original experiment, we discovered that administrative discrimination against Muslims could be driven by Islamophobic attitudes.
 Based on the two forms of bureaucratic discrimination defined in the original experiment, our study aims to assess perceptions about Muslims in Canada and discuss the potential for widespread administrative discrimination against Muslims.
@@
 In this paper, Olsen, Kyhse-Andersen, and Moynihan discuss the ethical significance of field experiments.
-However, they noted that they must proceed with this study given the policy importance that comes with understanding the barriers to school transfer for Muslim pupils in the Danish schools (CITATION).
+However, they noted that they must proceed with this study given the policy importance that comes with understanding the barriers to school transfer for Muslim pupils in the Danish schools [@originalpaper].
 In addition, to minimize risk, the authors anonymized individual responses in the replication data and communicated the results of the study to the Danish school administrators and relevant parties.
@@
 
-First, as stated in the original paper, 'the interaction with bureaucrats was limited to an initial response', meaning that it is unknown whether the bureaucrats would have accepted or declined a student in the unclear response case (CITATION).
+First, as stated in the original paper, 'the interaction with bureaucrats was limited to an initial response', meaning that it is unknown whether the bureaucrats would have accepted or declined a student in the unclear response case [@originalpaper].
 While the authors believe the evidence they have lends little support to this possibility, it may significantly skew the distribution of clear acceptances and clear rejections to communicate more substantiated findings.
 
-Second, there were more variables documented with respect to each email that was sent to a school, but were delinked with respect to the original email that was sent to a school to be compliant with GDPR in a Danish context (CITATION).
+Second, there were more variables documented with respect to each email that was sent to a school, but were delinked with respect to the original email that was sent to a school to be compliant with GDPR in a Danish context [@originalpaper].
 These variables included information about the email responder (gender, administrative status, whether they are Muslim or Danish) and information regarding the school (number of students enrolled, average grades of students enrolled, and the proportion of non-Danish students in the school).

### 2024-02-15 outputs/paper/paper.qmd
Final paper

@@
 format: pdf
-toc: true
+toc: false
 number-sections: true
@@
 These emails were sent under different names (Muslim/Danish), with 850 emails sent under one name and 848 under the other.
-Fictitious students were also assigned diligence traits, which could be discerned from the content of the emails (Overview of Senders’ and Respondents’ traits).
+Fictitious students were also assigned diligence traits, which could be discerned from the content of the emails (See Section 2.2.1).
 Additionally, the original study examined both the characteristics of the schools and those of the senders.
@@
 
-### Senders and Respondents'(schools) trait
+### Senders and Respondents' (Schools) trait {#sec-traits}
 
